test_imputed

### 2016-12-13 finalwriteup/trial_code.rmd
reset

ggplot(plot.pvals, aes(x = mod.vars, y = p.val)) + geom_boxplot() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1),
              panel.background = element_rect(fill = 'grey95')) +
        geom_hline(yintercept = 0.05, colour = 'red', linetype = 2) +
        scale_y_continuous(breaks = c(0, 0.05, .25, .5, .75, 1)) +
        labs(y = "P-value of F-statistic", x = "Independent Variables",
             title = "Summary of variable F-statistic P-values from ANOVA models")

@@

ggplot(data=cfor.varimp, aes(x=var, y=imp)) +
        theme(axis.text.x=element_text(angle=45,hjust=1)) +
        geom_bar(stat='identity') +
        labs(y = "Relative Variable Importance Value", x = "Independent Variables", title = "cForest Variable Importance Rankings of Complete Variables") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

ggplot(finance.plot, aes(x= threshold, y= profit.ratio, colour = method)) + 
        # geom_point(alpha = 0.005, shape = 16, size = 1) + 
        geom_hline(yintercept = 100, colour = "darkgray", linetype = 2) + 
        geom_hline(yintercept = 0, colour = "darkgray", linetype = 1) +
        stat_summary(fun.y = mean, 
                     fun.ymin = function(x) mean(x) - 1.96*sd(x),
                     fun.ymax = function(x) mean(x) + 1.96*sd(x),
                     fill = "gray", geom= "ribbon", alpha = 0.7, colour = NA) +
        stat_summary(fun.y = mean, geom="line") +
        scale_y_continuous(breaks = seq(0,110, by = 10)) + 
        scale_x_continuous(breaks = seq(0,1, by = .1)) +  
        theme(legend.position = "none",
              panel.background = element_rect(fill = 'gray95')) +
        labs(x = "Probability Threshold", 
             y = "Ratio of Model Profit to Historical Profit (%)",
             title = "Profit Curve for Blended and Individual Models") + 
        facet_wrap(~method, 
                   labeller = labeller( method = c("average" = "Simple Average Blend",
                                       "orig.boost"= "Orig. Boosted Trees",
                                       "orig.log" = "Orig. Logistic Regression",
                                       "orig.rf" = "Orig. Random Forest",
                                       "simp.log" = "Simple Log. Reg. Blend",
                                       "simp.boost" = "Simple Boosted Tree Blend",
                                       "comp.boost"= "Complex Boosted Tree Blend",
                                       "comp.rf"= "Complex randomForest Blend",
                                       "FWLS" = "FWLS"
                                       )))

@@

ggplot(finance.plot %>% filter(method == "simp.log"), 
       aes(x= threshold, y= profit.ratio, colour = method)) + 
        geom_hline(yintercept = 100, colour = "darkgray", linetype = 2) + 
        geom_hline(yintercept = 0, colour = "darkgray", linetype = 1) + 
        geom_point(alpha = 0.1, shape = 16) +
        stat_summary(fun.y = mean, 
                     fun.ymin = function(x) mean(x) - 1.96*sd(x),
                     fun.ymax = function(x) mean(x) + 1.96*sd(x),
                     fill = "gray", geom= "ribbon", alpha = 0.7, colour = NA) +
        stat_summary(fun.y = mean, geom="line") +
        scale_y_continuous(breaks = seq(0,110, by = 10)) + 
        scale_x_continuous(breaks = seq(0,1, by = .1)) + 
        theme(legend.position = "none", 
              panel.background = element_rect(fill = 'grey95')) +
        labs(x = "Probability Threshold", 
             y = "Ratio of Model Profit to Historical Profit (%)",
             title = "Profit Curve for Simple Logistic Regression Blended Model")

>>>>

ggplot(plot.pvals, aes(x = mod.vars, y = p.val)) + geom_boxplot() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1),
              panel.background = element_rect(fill = 'gray95')) +
        geom_hline(yintercept = 0.05, colour = 'red', linetype = 2) +
        scale_y_continuous(breaks = c(0, 0.05, .25, .5, .75, 1)) +
        labs(y = "P-value of F-statistic", x = "Independent Variables",
             title = "Summary of variable F-statistic P-values from ANOVA models")

@@

ggplot(data=cfor.varimp, aes(x=var, y=imp)) +
        theme(axis.text.x=element_text(angle=45,hjust=1),
              panel.background = element_rect(fill = 'gray95')) +
        geom_bar(stat='identity') +
        labs(y = "Relative Variable Importance Value", x = "Independent Variables", title = "cForest Variable Importance Rankings of Complete Variables") +
        theme(panel.background = element_rect(fill = 'gray95'))

@@

ggplot(finance.plot, aes(x= threshold, y= profit.ratio, colour = method)) + 
        # geom_point(alpha = 0.005, shape = 16, size = 1) + 
        geom_hline(yintercept = 100, colour = "darkgray", linetype = 2) + 
        geom_hline(yintercept = 0, colour = "darkgray", linetype = 1) +
        stat_summary(fun.y = mean, 
                     fun.ymin = function(x) mean(x) - 1.96*sd(x),
                     fun.ymax = function(x) mean(x) + 1.96*sd(x),
                     fill = "gray", geom= "ribbon", alpha = 0.7, colour = NA) +
        stat_summary(fun.y = mean, geom="line") +
        scale_y_continuous(breaks = seq(0,110, by = 20)) + 
        scale_x_continuous(breaks = seq(0,1, by = .2)) +  
        theme(legend.position = "none",
              panel.background = element_rect(fill = 'gray95')) +
        labs(x = "Probability Threshold", 
             y = "Ratio of Model Profit to Historical Profit (%)",
             title = "Profit Curve for Blended and Individual Models") + 
        facet_wrap(~method, 
                   labeller = labeller( method = c("average" = "Simple Average Blend",
                                       "orig.boost"= "Orig. Boosted Trees",
                                       "orig.log" = "Orig. Logistic Regression",
                                       "orig.rf" = "Orig. Random Forest",
                                       "simp.log" = "Simple Log. Reg. Blend",
                                       "simp.boost" = "Simple Boosted Tree Blend",
                                       "comp.boost"= "Complex Boosted Tree Blend",
                                       "comp.rf"= "Complex randomForest Blend",
                                       "FWLS" = "FWLS"
                                       )))

@@

ggplot(finance.plot %>% filter(method == "simp.log"), 
       aes(x= threshold, y= profit.ratio, colour = method)) + 
        geom_hline(yintercept = 100, colour = "darkgray", linetype = 2) + 
        geom_hline(yintercept = 0, colour = "darkgray", linetype = 1) + 
        geom_point(alpha = 0.1, shape = 16) +
        stat_summary(fun.y = mean, 
                     fun.ymin = function(x) mean(x) - 1.96*sd(x),
                     fun.ymax = function(x) mean(x) + 1.96*sd(x),
                     fill = "gray", geom= "ribbon", alpha = 0.7, colour = NA) +
        stat_summary(fun.y = mean, geom="line") +
        scale_y_continuous(breaks = seq(0,110, by = 10)) + 
        scale_x_continuous(breaks = seq(0,1, by = .1)) + 
        theme(legend.position = "none", 
              panel.background = element_rect(fill = 'grey95'),
              panel.grid.minor = element_blank()) +
        labs(x = "Probability Threshold", 
             y = "Ratio of Model Profit to Historical Profit (%)",
             title = "Profit Curve for Simple Logistic Regression Blended Model")

### 2016-12-13 model_blend.rmd
reset

Now narrow down which interaction terms to include
```{r}
fit2 <- aov(b.rpdol ~ b.timespan.cbrt + no.users + b.inv.log + Business + JD.Second + norm.log + norm.rf + norm.boost + b.timespan.cbrt*norm.log + no.users*norm.log + b.inv.log*norm.log + Business*norm.log + JD.Second*norm.log + b.timespan.cbrt*norm.rf + no.users*norm.rf + b.inv.log*norm.rf + Business*norm.rf + JD.Second*norm.rf + b.timespan.cbrt*norm.boost + no.users*norm.boost + b.inv.log*norm.boost + Business*norm.boost + JD.Second*norm.boost + Discipline*norm.boost + Discipline*norm.log + Discipline*norm.rf,
                                   data = all10.blend)

>>>>

Now narrow down which interaction terms to include
```{r}
fit2 <- glm(b.rpdol ~ b.timespan.cbrt + no.users + b.inv.log + Business + JD.Second + norm.log + norm.rf + norm.boost + b.timespan.cbrt*norm.log + no.users*norm.log + b.inv.log*norm.log + Business*norm.log + JD.Second*norm.log + b.timespan.cbrt*norm.rf + no.users*norm.rf + b.inv.log*norm.rf + Business*norm.rf + JD.Second*norm.rf + b.timespan.cbrt*norm.boost + no.users*norm.boost + b.inv.log*norm.boost + Business*norm.boost + JD.Second*norm.boost + Discipline*norm.boost + Discipline*norm.log + Discipline*norm.rf, family = binomial(),
                                   data = all10.blend)

backwards = step(fit2)
formula(backwards)

### 2016-12-13 prob_review.rmd
reset

```{r_loadpackages, echo=FALSE, include=FALSE}
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library('ggplot2',lib='C:/Progra~1/R/R-3.2.1/library')
library('gbm', lib = 'C:/Progra~1/R/R-3.2.2/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.2/library')
library('caret', lib = 'C:/Progra~1/R/R-3.2.2/library')
library('pROC',lib='C:/Progra~1/R/R-3.2.2/library')

@@

@@

                        } else {
                                if(method %in% 'log'){
                                        fit<- glm(as.formula(formula), 
                                                  data = df[-folds[[j]],], family = binomial())
                                        pred <- predict(fit, test,
                                                        type = "response")
                                } else {
                                        fit <- gbm(as.formula(formula), data = df[-folds[[j]],],
                                                   distribution = "bernoulli", n.trees = 10000,
                                                   shrinkage = 0.001, interaction.depth = 4,
                                                   n.minobsinnode = 20)

@@

>>>>

```{r_loadpackages, echo=FALSE, include=FALSE}
library("plyr",lib = 'C:/Progra~1/R/R-3.2.3/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.3/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.3/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.3/library')
library('ggplot2',lib='C:/Progra~1/R/R-3.2.3/library')
library('gbm', lib = 'C:/Progra~1/R/R-3.2.3/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.3/library')
library('caret', lib = 'C:/Progra~1/R/R-3.2.3/library')
library('pROC',lib='C:/Progra~1/R/R-3.2.3/library')

@@

        #order levels
        df <- within(df, b.timespan.cbrt <- factor(b.timespan.cbrt, 
                                               levels=c('1d-3wk', '3wk-2.5m','2.5m-9m','9m-1.5y','1.5y-3y','>3y')))
        df <- within(df, majority.pos <- factor(majority.pos, 
                                               levels=c('contracttech', 'midtech','seniortech','gradpro',
                                                        'midpro','seniorpro','director')))

        levels(df$b.timespan.cbrt) <- c('1d-3wk', '3wk-2.5m','2.5m-9m','9m-1.5y','1.5y-3y','>3y')
        df$b.timespan.cbrt <- ordered(df$b.timespan.cbrt)

@@

                        } else {
                                if(method %in% 'log'){
                                        fit<- glm(as.formula(formula), 
                                                  data = df[-folds[[j]],], family = binomial())
                                        pred <- predict(fit, test,
                                                        type = "response")
                                } else {
                                        fit <- gbm(as.formula(formula), data = df, #[-folds[[j]],],
                                                   distribution = "bernoulli", n.trees = 10000,
                                                   shrinkage = 0.001, interaction.depth = 4,
                                                   n.minobsinnode = 20)

@@

#partial dependence plot for boosted only
fit$var.names
i=5
a<- plot.gbm(fit, i, type="response")
a

### 2016-12-13 rand_forest.rmd
reset

>>>>

New analysis for thesis write up

#make new dataframe for future use with normalised variables and variables that you want to use only
all8a<- all7d %>% select(no.users, Discipline, pc.pro, Business, code.client, JD.Second, timespan.cbrt,
                         inv.mlsto.log,client.totinv.log, pc.majpos.log, code.contact, Billing.Type,
                         majority.pos, return.pdol, mlsto, Year)
write.csv(all8a, 'C:/Users/n9232371/Documents/Consultbusiness/data/all8a.csv')
all8a <- read.csv("~/OneDrive/shared files/Bligh Tanner/masters/data/all8a.csv")

RMSE<- function(answer, guess){
        error= answer-guess
        root.error= sqrt(mean(error^2))
        return(root.error)
}

final.rf.output<- function(df=all8a, no.tests = 50, core = TRUE) {

        summary.tests = matrix(NA, nrow = no.tests, ncol = 3)

        for(i in 1:no.tests){

        if(core == FALSE){
        samp = sample.int(nrow(df), 1)                        
        #create sample df - use all variables that are complete from a sample row of data
        sample = df[samp,]
        sample = sample[,!is.na(sample)]
        vars= names(sample)
        vars = vars[! vars %in% c('mlsto','Year','return.pdol')]
        variables = vars
        } else{
                variables = c('inv.mlsto.log', 'Discipline', 'timespan.cbrt',
                              'no.users', 'pc.pro', 'Business')
        }

        if('code.client' %in% variables){
        sample = factor(sample(unique(reduced$code.client),size=53,
                                     replace=FALSE))
        reduced= reduced[reduced$code.client %in% sample,]

        if('code.contact' %in% variables){
        sample1 = factor(sample(unique(reduced$code.contact),size=53,
                                     replace=FALSE))
        reduced= reduced[reduced$code.contact %in% sample1,]

        for(j in 1:length(variables)){
                formula = paste(formula, variables[j], sep= " + ")
        }

        samp_size = floor(0.75*nrow(reduced))
        create.train = base::sample.int(nrow(reduced), samp_size)
        train.df = reduced[create.train,]
        test.df = reduced[-create.train,]

        cats = c('code.client', 'code.contact', 'JD.Second', 'Business', 'majority.pos')
        for(k in seq_along(cats)){
                if(cats[k] %in% variables){
                test.df = test.df[test.df[,cats[k]] %in% unique(train.df[,cats[k]]),]
        }
        }

        final = randomForest(as.formula(formula), data= train.df, mtry=5,ntree=500, importance=FALSE)

        ans = data.frame(answer= test.df$return.pdol, final.lm = predict(final, test.df))

        test.df$predict= ans$final.lm

        #random RMSE
        r= mean(reduced$return.pdol)
        random.RMSE= RMSE(reduced$return.pdol, r) %>% round(3)

        #final RMSE for all rows in reduced in a regression
        final.RMSE= RMSE(ans$answer, ans$final.lm) %>% round(3)

        summary.tests[i,1]= random.RMSE
        summary.tests[i,2]= final.RMSE
        summary.tests[i,3]= nrow(test.df)

        #track progress
        cat(i," ")
        }
        summary.tests = as.data.frame(summary.tests)
        names(summary.tests) = c('random.RMSE', 'final.RMSE', 'test.nrow')
        return(summary.tests)
}

#how many tests required? power calculation
n.samples = function(data = results.core$diff, type.calc = 'one.sample', alt = 'greater'){
        d.calc = abs(mean(data))/sd(data)
        pow_pow = pwr.t.test(n = NULL, d = d.calc , sig.level = 0.05, power = .8, type = c(type.calc), alternative = alt)
        return(ceiling(pow_pow$n))
}

n.samples(data = results.core$diff)
n.samples(data = results$diff)

# 3 tests required for results.core

results = final.rf.output(df=all8a, no.tests = 100, core = FALSE)
results = results %>% mutate(diff = random.RMSE - final.RMSE)
results = results %>% filter(diff>-25)
results.core = final.rf.output(df=all8a, no.tests = 50, core = TRUE)
results.core = results.core %>% mutate(diff = random.RMSE - final.RMSE)
saveRDS(results, "~/Documents/github/consult/finalwriteup/report_data/reg_rf.rds")
saveRDS(results.core, "~/Documents/github/consult/finalwriteup/report_data/reg_rf_core.rds")

results.core %>% ggplot(., aes(x = test.nrow, y = final.RMSE)) + geom_point()

#histogram of difference
results %>% ggplot(., aes(x =diff, y = ..density..)) + geom_histogram() + geom_density()

# t- test
t_test = t.test(results$diff, alternative = "greater", mu = 0)
str(t_test)
t_test$p.value
```

### 2016-12-13 rf_log_naiive_auc.rmd
reset

# n.samples function is defined in 'draft.rmd'
index = c(1,3,4)
ns = NULL
for(i in seq_along(index)){
        temp = n.samples(data = tot.auc.m[c(2, index[i])], type.calc = 'two.sample', alt = 'two.sided')
        ns[i] = temp
}
ns

>>>>

# n.samples function is defined in 'draft.rmd'
index = c(1,3,4)
ns = NULL
for(i in seq_along(index)){
        temp = n.samples(data = reduc.totAUC[c(2, index[i])], type.calc = 'two.sample', alt = 'two.sided')
        ns[i] = temp
}
ns
